The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-12-04 paper/ms.tex
mu

This paper is paper is structured as follows. In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. We also list the different physical parameters in
the simulated grid of models. In the next \S \ref{sec:results} we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the sphere
rotational velocity. In \S \ref{sec:discussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modeling of the \ly line. In the last section we present
our conclusions.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{WidthVvsVmax.png}
    \caption{Half-width for the non-dusty models as a function of
      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
      correspond to homogeneous (central) source
      distributions. \label{fig:widthvsvelocity}} 
\end{figure}

@@

In the the off-center emission the variations  in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer. The most
interesting effect is that emission is that in  some models ($\tau =
10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
presents three peaks (blue-shifted,centered, red-shifted). However, we
do not find any asymmetry in the line produced by the off-center
emission. As in the homogeneous / central model the line gets broader
as the rotational velocity increases.

The results for the off-centered spheres placed closed to the center
at $C=\pm 0.25R$ do not display the features discussed above for the
spheres at $C=\pm0.5R$.

>>>>

This paper is structured as follows. In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. We also list the different physical parameters in
the simulated grid of models. In the next \S \ref{sec:results} we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the sphere
rotational velocity. In \S \ref{sec:discussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modeling of the \ly line. In the last section we present
our conclusions.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.png}
    \caption{Half-width for the non-dusty models as a function of
      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
      correspond to homogeneous (central) source
      distributions. \label{fig:widthvsvelocity}} 
\end{figure}

@@

In the off-centre emission the variations in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer. The most
interesting effect is that emission is that in  some models ($\tau =
10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
presents three peaks (blue-shifted,centred, red-shifted). However, we
do not find any asymmetry in the line produced by the off-center
emission. As in the homogeneous / central model the line gets broader
as the rotational velocity increases.

The results for the off-centred spheres placed closer to the centre
at $C=\pm 0.25R$ do not display such a stronger features discussed above for the
spheres at $C=\pm0.5R$, there is only one model which slightly shows a 
three peak morphology with $\mathrm{V=300km s^{1}}$ and $\tau = 10^{7}$.
